|

### 2024-08-11 doc/paper.qmd
deleted test EM1,2

with open('../data/generated/table_1.pickle', 'rb') as f:
    results = pickle.load(f)

@@

Table 1 provides descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score, where countries are sorted in descending order based on their aggregate score. The discussion on replication findings is presented in @sec-results.

## delete from fikir.
```{python}
#| echo: false
#| output: asis

print(prep_latex_table(
    results['replication_results'],
    caption='Replicated table - P/B Ratios And Future Residual Income',
    label='tab:replicated_penman'
))
```

@@

Moreover, the configuration file utilized additional refinements as proposed by @WRDS_Overview_2024. Specifically, using "A" (Annual) in the `freq` variable ensured that the data represents financial information reported on an annual basis, consistent with the methodology outlined in the paper by @Leuz_2003. This excludes data reported on a current, daily, or quarterly basis. After retaining only relevant company data, filtering out financial institutions, and focusing on the specified countries, the processed data was saved to a CSV file in the `data/pulled` directory, as specified in the configuration file `config/pull_data_cfg`​.

@@

1.	Compute Accruals by using changes in various components of a firm’s balance sheet and income statement, such as total current assets, cash, current liabilities, short-term debt, taxes payable, and depreciation:
$$
\begin{aligned}
\text{Accruals}_{it} &= (\Delta \text{CA}_{it} - \Delta \text{Cash}_{it}) - (\Delta \text{CL}_{it} - \Delta \text{STD}_{it} - \Delta \text{TP}_{it}) - \text{Dep}_{it} 
& \\
\text{where:} \\
\Delta \text{CA}_{it} & = \text{Change in total current assets} \\
\Delta \text{Cash}_{it} & = \text{Change in cash and cash equivalents} \\
\Delta \text{CL}_{it} & = \text{Change in total current liabilities} \\
\Delta \text{STD}_{it} & = \text{Change in short-term debt included in current liabilities} \\
\Delta \text{TP}_{it} & = \text{Change in income taxes payable} \\
\text{Dep}_{it} & = \text{Depreciation and amortization expense for firm i in year t} 
\end{aligned}
$$

@@

EM4 is calculated as the ratio of the number of small profits to the number of small losses for each country, where small profits and small losses are determined by scaling net earnings by lagged total assets:
$$
\begin{aligned}
\text{EM4}&= \frac{\text{Small Profits}}{\text{Small Losses}} \\
& \\
\text{where:} \\
\text{Small Profits} & : \frac{\text{Net Earnings}_{it}}{\text{Total Assets}_{it-1}} \in [0, 0.01] \\
\text{Small Losses}  & : \frac{\text{Net Earnings}_{it}}{\text{Total Assets}_{it-1}} \in [-0.01, 0) \\
\end{aligned}
$$

>>>>

# Load the results from the existing pickle file for table_1
with open('../data/generated/table_1.pickle', 'rb') as f:
    results = pickle.load(f)

# Load the results from the new pickle file for final_table and summary_stats
with open('../output/em_results.pickle', 'rb') as f:
    em_results = pickle.load(f)

@@

Table 1 provides descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score, where countries are sorted in descending order based on their aggregate score. The discussion on replication findings is presented in @sec-results.
```{python}
#| label: final_table 
#| echo: false
#| output: asis

print(prep_latex_table(
    em_results['final_table'],
    caption='Replicated table - EM1, EM2, EM3, EM4, and Aggregate EM Score',
    label='tab:final_table'
))
```

```{python}
#| label: summary_stats 
#| echo: false
#| output: asis

print(prep_latex_table(
    em_results['summary_stats'],
    caption='Replicated table - Summary Statistics for EM1, EM2, EM3, and EM4',
    label='tab:summary_stats'
))
```

@@

Moreover, the configuration file utilized additional refinements as proposed by @WRDS_Overview_2024. Specifically, using "A" (Annual) in the `freq` variable ensured that the data represents financial information reported on an annual basis, consistent with the methodology outlined in the paper by @Leuz_2003. This excludes data reported on a current, daily, or quarterly basis. After retaining only relevant company data, filtering out financial institutions, and focusing on the specified countries, the processed data was saved to a CSV file in the `data/pulled` directory, as specified in configuration file `config/pull_data_cfg`​.

@@

1.	Compute Accruals by using changes in various components of a firm’s balance sheet and income statement, such as total current assets, cash, current liabilities, short-term debt, taxes payable, and depreciation:

$$
\begin{aligned}
\text{Accruals}_{it} &= (\Delta \text{CA}_{it} - \Delta \text{Cash}_{it}) - (\Delta \text{CL}_{it} - \Delta \text{STD}_{it} - \Delta \text{TP}_{it}) - \text{Dep}_{it} 
& \\
\text{where:} \\
\Delta \text{CA}_{it} & = \text{Change in total current assets} \\
\Delta \text{Cash}_{it} & = \text{Change in cash and cash equivalents} \\
\Delta \text{CL}_{it} & = \text{Change in total current liabilities} \\
\Delta \text{STD}_{it} & = \text{Change in short-term debt included in current liabilities} \\
\Delta \text{TP}_{it} & = \text{Change in income taxes payable} \\
\text{Dep}_{it} & = \text{Depreciation and amortization expense for firm i in year t} 
\end{aligned}
$$

@@

EM4 is calculated as the ratio of the number of small profits to the number of small losses for each country, where small profits and small losses are determined by scaling net earnings by lagged total assets:
$$
\text{EM4} = \frac{\text{Small Profits}}{\text{Small Losses}}
$$
$$
\begin{alignedat}{2}
\text{where:} \\ \quad & \text{Small Profits} && = \frac{\text{Net Earnings}_{it}}{\text{Total Assets}_{it-1}} \in [0, 0.01] \\
& \text{Small Losses} && = \frac{\text{Net Earnings}_{it}}{\text{Total Assets}_{it-1}} \in [-0.01, 0)
\end{alignedat}
$$
